k-Space Domain Parallel Transmit Pulse Design

### 2020-09-10 Manuscript/Method.tex
wag further results edits

\subsection*{L-Curves}
To compare the tradeoff between excitation error and integrated RF power for spatial and k-space domain designs,
pulse designs were repeated while varying Tikhonov regularization parameters ($\lambda$ in Equation \ref{eq:Solution}) 
over five orders of magnitude. 
The k-space domain designs were repeated four times to investigate the three main sources of error:
finite patch width, finite inclusion width, and $B_1^+$ map product interpolation. 
Specifically, a design was performed using patch and inclusion widths of four
with interpolated $B_1^+$ map products (`Interpolated $\bm{S}^H\bm{S}$ matrices'),
patch and inclusion widths covering the entire design grid with interpolated $B_1^+$ map products,
patch and inclusion widths of four without $B_1^+$ map product interpolation (`Exact $\bm{S}^H\bm{S}$ matrices'; 
$B_1^+$ maps were phase-modulated to each trajectory location before Fourier transform),
and patch and inclusion widths covering the entire design grid without $B_1^+$ map product interpolation. 
Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.

>>>>

\subsection*{L-Curves}
To compare the tradeoff between excitation error (measured by root-mean-square error)
and integrated RF root-mean-square (RMS) amplitude for spatial and k-space domain designs,
pulse designs were repeated while varying Tikhonov regularization parameters ($\lambda$ in Equation \ref{eq:Solution}) 
over five orders of magnitude. 
The k-space domain designs were repeated four times to investigate the three main sources of error:
finite patch width, finite inclusion width, and $B_1^+$ map product interpolation. 
Specifically, a design was performed using patch and inclusion widths of four
with interpolated $B_1^+$ map products (`Interpolated $\bm{S}^H\bm{S}$ matrices'),
patch and inclusion widths covering the entire design grid with interpolated $B_1^+$ map products,
patch and inclusion widths of four without $B_1^+$ map product interpolation (`Exact $\bm{S}^H\bm{S}$ matrices'; 
$B_1^+$ maps were phase-modulated to each trajectory location before Fourier transform),
and patch and inclusion widths covering the entire design grid without $B_1^+$ map product interpolation. 
Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.
For each design, flip angle RMSE (calculated using the spatial domain non-uniform fast Fourier transform) and root-mean-square RF amplitude was
calculated.

### 2020-09-10 Manuscript/Result.tex
wag further results edits

\subsection*{L-Curves}

>>>>

\subsection*{L-Curves}
Figure \ref{fig:LCurves} plots flip angle RMSE versus RF RMS amplitude for the spatial domain method
and different configurations of the k-space domain method.
The spatial domain method achieves the best overall tradeoff between error and RMS amplitude (dashed black curve),
which is matched by the k-space domain method when all target locations are solved simultaneously with
all excitation trajectory points included (orange curve) and exact $\bm{S}^H\bm{S}$ matrix construction. 
When the inclusion and patch widths are limited to 4 cycles/FOV but the $\bm{S}^H\bm{S}$ 
matrices are still constructed exactly, there is an increase in error and RMS amplitude (solid blue curve). 
However, a larger penalty is incurred by interpolating the entries of the $\bm{S}^H\bm{S}$ matrices (dashed orange curve)
than by limiting the inclusion and patch widths.
Combining interpolation of the $\bm{S}^H\bm{S}$ matrix entries and patch and inclusion widths of 4 cycles/FOV yield 
the dashed blue curve, which has a higher error and RF amplitude than when interpolation or small patch and inclusion widths are
used alone.
Overall, these results and the results in Figure \ref{fig:ComputationTime} and Table \ref{fig:wsize}
show that the k-space domain method allows a tradeoff between computation time and memory usage versus
excitation error and RMS RF amplitude.
The dots on the spatial domain and k-space domain curves indicate the knees of of the curves corresponding to
the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, \ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.
